\documentclass[../main.tex]{subfiles}

\begin{document}

\begin{thebibliography}{999}

\bibitem{ruder17}
  S. Ruder,
  \emph{An overview of gradient descent optimization algorithms}.
  arXiv:1609.04747v2 [cs.LG],
  15 Jun 2017.

\bibitem{hinton17}
  G. Hinton, N. Srivastava, K. Swersky,
  \emph{Overview of mini-batch gradient descent}.
  University of Toronto
  [online lecture notes]
  2017.
  \url{https://www.cs.toronto.edu/~tijmen/csc321/slides/lecture_slides_lec6.pdf}.

\bibitem{kingma17}
  D.P. Kingma, J.L. Ba,
  \emph{Adam: A Method for Stochastic Optimization}.
  arXiv:1412.6980v9 [cs.LG],
  30 Jan 2017.

\bibitem{kennedy12}
  J. Kennedy, R. Eberhart,
  \emph{Particle Swarm Optimisation}.
  Washington, DC,
  2012.

\bibitem{carr14}
  J. Carr,
  \emph{An Introduction to Genetic Algorithms}
  [online].
  May 16, 2014,
  \url{https://www.whitman.edu/Documents/Academics/Mathematics/2014/carrjk.pdf}.

\bibitem{hornik91}
  K. Hornik,
  \emph{Approximation Capabilities of Multilayer Feedforward Networks}.
  Neural Networks,
  1991,
  Volume 4,
  Issue 2,
  Pages 251-257.

\bibitem{liang17}
  S. Liang, R. Srikant,
  \emph{Why Deep Neural Networks for Function Approximation?}.
  arXiv:1610.04161v2 [cs.LG],
  3 Mar 2017.

\bibitem{caruana01}
  R. Caruana, S. Lawrence, L. Giles,
  \emph{Overfitting in Neural Nets: Backpropagation, Conjugate Gradient, and Early Stopping}.
  NIPS,
  2001.

\bibitem{goodfellow16}
  I. Goodfellow, Y. Bengio, A. Courville,
  2016.
  \emph{Deep Learning}
  [online],
  MIT Press.
  \url{http://www.deeplearningbook.org/contents/regularization.html}.

\bibitem{srivastava14}
  N. Srivastava, G. Hinton, A. Krizhevsky, I. Sutskever, R. Salakhutdinov,
  \emph{Dropout: A Simple Way to Prevent Neural Networks from Overfitting}.
  Journal of Machine Learning Research, 
  15 (Jun): 1929-1958, 2014.

\bibitem{ioffe15}
  S. Ioffe, C. Szegedy,
  \emph{Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift}.
  arXiv:1502.03167v3 [cs.LG],
  2 Mar 2015.

\bibitem{li18}
X. Li, S. Chen, X. Hu, J. Yang,
\emph{Understanding the Disharmony between Dropout and Batch Normalization by Variance Shift}.
arXiv:1801.05134v1 [cs.LG],
16 Jan 2018.

\bibitem{giryes16}
  R. Giryes, G. Sapiro, A.M. Bronstein,
  \emph{Deep Neural Networks with Random Gaussian Weights: A Universal Classification Strategy?}.
  arXiv:1504.08291v5 [cs.NE],
  14 Mar 2016.

\bibitem{zur09}
  R.M. Zur, Y. Jiang, L.L. Pesce, K. Drukker,
  \emph{Noise injection for training artificial neural networks: A comparison with weight decay and early stopping}.
  Med Phys.
  2009 Oct;
  36(10): 4810–4818.

\bibitem{nah18}
  S. Nah, T.H. Kim, K.M. Lee,
  \emph{Deep Multi-scale Convolutional Neural Network for Dynamic Scene Deblurring}.
  arXiv:1612.02177v2 [cs.CV],
  7 May 2018.

\bibitem{nguyen16}
  T. Nguyen, K. Mori, R. Thawonmas,
  \emph{Image Colourization Using a Deep Convolutional Neural Network}.
  ASIAGRAPH Conference,
  2016.

\bibitem{rumelhart86}
  D.E. Rumelhart, G. Hinton, R.J. Williams,
  \emph{Learning internal representations by error propagation}.
  Parallel Distributed Processing,
  Vol 1: Foundations,
  MIT Press,
  Cambridge, MA,
  1986.

\bibitem{vincent08}
  P. Vincent, H. Larochelle, Y. Bengio, P. Manzagol,
  \emph{Extracting and Composing Robust Features with Denoising Autoencoders}.
  Universit\'e de Montr\'eal,
  2008.

\bibitem{kingma14}
  D.P. Kingma, M. Welling,
  \emph{Auto-Encoding Variational Bayes}.
  arXiv:1312.6114v10 [stat.ML],
  1 May 2014.

\bibitem{higgins16}
  I. Higgins, L. Matthey, A. Pal, C. Burgess, X. Glorot, M. Botvinik, S. Mohamed, A. Lerchner,
  \emph{beta-VAE: Learning Basic Visual Concepts with a Constrained Variational Framework}.
  ICLR,
  04 Nov 2016.

\bibitem{goodfellow14}
  I. Goodfellow, J. Pouget-Abadie, M. Mirza, B. Xu, D. Warde-Farley, S. Ozair, A. Courville, Y. Bengio,
  \emph{Generaitve Adversarial Nets}.
  arXiv:1406.2661v1 [stat.ML],
  10 Jun 2014.

\bibitem{horger18}
  F. Horger, T. W\"urfl, V. Christlein, A. Maier,
  \emph{Deep Learning for Sampling from Arbitrary Probability Distributions}.
  arXiv:1801.04211v2 [cs.LG],
  10 Jul 2018.

\bibitem{ledig17}
  C. Ledig, L. Theis, F. Husz\'ar, J. Caballero, A. Cunningham, A. Acosta, A. Aitken, A. Tejani, J. Totz, Z. Wang, W. Shi,
  \emph{Photo-Realistic Single Image Super-Resolution Using a Generative Adversarial Network}.
  arXiv:1609.04802v5 [cs.CV],
  25 May 2017.

\bibitem{zhu18}
  J. Zhu, R. Park, P. Isola, A.A. Efros,
  \emph{Unpaired Image-to-Image Translation using Cycle-Consistent Adversarial Networks}.
  arXiv:1703.10593v6 [cs.CV],
  15 Nov 2018.

\bibitem{anirudh18}
  R. Anirudh, J.J. Thiagarajan, B. Kailkhura, T. Bremer,
  \emph{An Unsupervised Approach to Solving Inverse Problems using Generative Adversarial Networks}.
  arXiv:1805.07281v2 [cs.CV],
  4 Jun 2018.

\bibitem{bang18}
  D. Bang, H. Shim,
  \emph{MGGAN: Solving Mode Collapse using Manifold Guide Training}.
  arXiv:1804.04391v1 [cs.CV],
  12 Apr 2018.

\bibitem{hochreiter97}
  S. Hochreiter, J. Schmidhuber,
  \emph{Long Short-Term Memory}.
  Neural Computation,
  Volume 9 Issue 8,
  15 November 1997.

\bibitem{socher11}
  R. Socher, C.C. Lin, A.Y. Ng, C.D. Manning,
  \emph{Parsing Natural Scenes and Natural Language with Recursive Neural Networks}.
  Stanford University,
  2011.

\bibitem{mikolov13}
  T. Mikolov, K. Chen, G. Corrado, J. Dean,
  \emph{Efficient Estimation of Word Representations in Vector Space}.
  arXiv:1301.3781v3 [cs.CL],
  7 Sep 2013.

\bibitem{le14}
  Q. Le, T. Mikolov,
  \emph{Distributed Representations of Sentences and Documents}.
  arXiv:1405.4053v2 [cs.CL],
  22 May 2014.

\bibitem{sigmund01}
  O. Sigmund,
  \emph{A 99 line topology optimization code written in Matlab}.
  Struct Multidisc Optim 21,
  120-127,
  2001.

\bibitem{raudys91}
  S.J. Raudys, A.K. Jain,
  \emph{Small Sample Size Effects in Statistical Pattern Recognition: Recommendations for Practitioners}.
  IEEE Transactions on Pattern Analysis and Machine Intelligence,
  Vol. 13, No. 3,
  3 March 1991.

\bibitem{ou07}
  G. Ou, Y.L. Murphey,
  \emph{Multi-class pattern classification using neural networks}.
  Pattern Recognition,
  Volume 40, Issue 1, Pages 4-18,
  2007.

\bibitem{mnih15}
  V. Mnih, K. Kavukcuoglu, D. Silver, A. Graves, I. Antonoglou, D. Wierstra, M. Riedmiller,
  \emph{Playing Atari with Deep Reinforcement Learning}.
  2015.

\bibitem{park91}
  J. Park, I.W. Sandberg,
  \emph{Universal Approximation Using Radial-Basis-Function Networks}.
  Neural Computation,
  Volume 3, Issue 2,
  June 1991.

\bibitem{bengio94}
  Y. Bengio, P. Simard, P. Frasconi,
  \emph{Learning long-term dependencies with gradient descent is difficult}.
  IEEE Trans Neural Netw.,
  Volume 5, Issue 2,
  1994.

\bibitem{robert16}
  C.P. Robert,
  \emph{The Metropolis-Hastings algorithm}.
  arXiv:1504.01896v3 [stat.CO],
  27 Jan 2016.

\bibitem{wildberger12}
  N.J. Wildberger,
  \emph{Simplices and simplicial complexes}.
  \url{https://www.youtube.com/watch?v=Uq4dTjHfLpI},
  7 Oct 2012.

\bibitem{agarap19}
  A.F.M. Agarap,
  \emph{Deep Learning using Rectified Linear Units (ReLU)}.
  arXiv:1803.08375v2 [cs.NE],
  7 Feb 2019.

% Unused references:

\bibitem{luo18}
  R. Luo, F. Tian, T. Qin, E. Chen, T. Yiu,
  \emph{Neural Architecture Optimization}.
  arXiv:1808.07233v4 [cs.LG],
  31 Oct 2018.

\bibitem{yu18}
  Y. Yu, T. Hur, J. Jung, I.G. Jang,
  \emph{Deep learning for determining a near-optimal topological design without any iteration}.
  Springer Nature,
  2018.

\end{thebibliography}
\end{document}
